### 2019-03-14 papers/journal/problem.tex
minor update

\subsubsection{$\fbmc$ Search problem.}
For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth $w$,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected, within $w$ depth of unwinding.

\subsubsection{$\fsmt$ Search problem.}
For a given $k$, size $\nu$, and molecule number $\mu$,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$, and
$G$ is not $k$-connected.

>>>>

\subsubsection{$\fbmc$ search problem.}
For a given $k$, size $\nu$, molecule number $\mu$, and unwinding depth $w$,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$, and $G$ is not $k$-connected, within $w$ depth of unwinding.

\subsubsection{$\fsmt$ search problem.}
For a given $k$, size $\nu$, and molecule number $\mu$,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$, and
$G$ is not $k$-connected.
